Programs Performance Analysis Toolkit

### 2013-09-30 keynote/Keynote.tex
Translate existing keynote to English

\title{Инструментарий моделирования быстродействия программ}
\author{Михаил Панков}
\institute{МГТУ им Н.Э.Баумана}
\date{19 июня 2013 года}

@@

\begin{frame}
\frametitle{Цель, задачи, и актуальность темы работы}

\begin{block}{Цель}
	\begin{itemize}
		\item Разработать метод и ПО (инструментарий) моделирования быстродействия программ на компьютерах общего назначения
	\end{itemize}
\end{block}

\begin{block}{Задачи}
	\begin{enumerate}
		\item Разработать метод моделирования быстродействия программ
		\item Выполнить программную реализацию инструментария, позволяющего оценивать быстродействие программ и осуществлять его моделирование
		\item Исследовать эффективность инструментария моделирования быстродействия программ на тестовом наборе программ
	\end{enumerate}
\end{block}

\begin{block}{Актуальность}
	\begin{enumerate}
		\item Оценка эффективности компьютера на этапе его проектирования или приобретения
		\item Поиск оптимальных настроек компилятора при итеративной
	\end{enumerate}
\end{block}

>>>>

\title{Programs Performance Analysis Toolkit}
\author{Michael Pankov}
\institute{Bauman Moscow State Technical University}
\date{June 19, 2013}

@@

\begin{frame}
\frametitle{Goal, tasks, and importance of the work}

\begin{block}{Goal}
	\begin{itemize}
		\item Develop a method and software toolkit for modeling of programs performance on general purpose computers
	\end{itemize}
\end{block}

\begin{block}{Tasks}
	\begin{enumerate}
		\item Develop method of programs performance modeling 
		\item Implement the programs performance analysis \& modeling toolkit
		\item Study the efficiency of programs performance modeling toolkit on a set of benchmarks
	\end{enumerate}
\end{block}

\begin{block}{Importance}
	\begin{enumerate}
		\item Estimation of computer performance during its design (see co-design)
		\item Search of optimal compiler settings by methods of iterative compilation and machine learning-driven techniques
	\end{enumerate}
\end{block}
